Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
update results together with Tyler

>>>>

\paragraph{Performance}
\myfig~\ref{fig:} reports the overhead brought by the scheduling of
non-cooperative kernels over the cooperative kernel execution time
(geometric mean over all applications and inputs on the Iris chip, other
chips look similar\HEComment{We can put the graphs of ther chips in
appendix}), along with the period (aritmetic mean over all applications
and inputs) at which non-cooperative kernels can be scheduled. We show
results for the three workloads listed in
\mysec~\ref{sec:sizingnoncoop}. The two gray horizontal lines in the
period graph correspond to the period goals of the workloads: the higher
(resp. lower) line corresponds to a period of 70ms (resp. 40ms) for the
light (resp. medium and heavy) workload.

Non-cooperative kernels running a workload with a single workgroup leads
to almost no overhead, but the period is far too high to meet the needs
of any of our three workloads. For example, a heavy workload averages a
period of 939 ms. As more workgroups are dedicated to non-cooperative
kernels, they execute quickly enough to be scheduled at the expected
period. More concretely, for the light and medium workloads, a quarter
of the workgroups executing the non-cooperative kernel are able to meet
their goal period (70 and 40 ms resp.). However, a quarter of the
workgroups are not sufficient to meet the goal for the heavy workload
(giving a mean period of 88 ms). Finally, if half of the workgroups are
allocated to the non-cooperative kernel, the heavy workload gets
averages \~10\% over its goal period (mean of 44 ms). If asking for all
but one, the heavy workload can reach its goal period.

Yet, as expected, allocating more non-cooperative workgroups increases
the execution time overhead of the cooperative kernel. Still the heavy
workloads meet their period (by allocating all but one workgroup for
non-cooperative kernels) for an overhead less than 1.4 on average. Light
and medium workloads meet their period with only a negligable overhead
of the cooperative kernel (less than 1.03 slowdown).
